### 2022-06-27 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@e9d427c180600ce8759a5f59777d64c33b08a09b 🚀

Subsequently, we tested the hypothesis that the biogeography of bat
betacoronaviruses should track the biogeography of their hosts. To test
this idea, we loosely adapted a method from,\textsuperscript{65,66} who
proposed a phylogenetic method for the delineation of animal
biogeographic regions. In their original method, a distance matrix -
where each row or column represents a geographic raster's grid cell, and
the dissimilarity values are the ``beta diversity similarity'' of their
community assemble - undergoes non-metric multidimensional scaling
(NMDS); the first two axes of the NMDS are projected geographically
using a four-color bivariate map. Here, we build on this idea with an
entirely novel methodology. First, we measure the phylogenetic distance
between the different viruses in the betacoronaviruses tree by using the
cophenetic function in \texttt{ape};\textsuperscript{67} subsequently,
we take a principal components analysis of that distance matrix (readily
interchangeable for NMDS in this case) to project the viral tree into an
n-dimensional space. We then take the first two principal components
and, as with the evolutionary distinctiveness analysis, aggregated these
to a mean host value and projected them using a four-color bivariate
map.

@@

\leavevmode\hypertarget{ref-VanBrussel2022ZooDis}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Van Brussel, K. \& Holmes, E. C. Zoonotic disease and
virome diversity in bats. \emph{Current Opinion in Virology}
\textbf{52}, 192--202 (2022).}

\leavevmode\hypertarget{ref-Letko2020BatVir}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Letko, M., Seifert, S. N., Olival, K. J., Plowright, R.
K. \& Munster, V. J. Bat-borne virus diversity, spillover and emergence.
\emph{Nature Reviews Microbiology} \textbf{18}, 461--471 (2020).}

\leavevmode\hypertarget{ref-Banerjee2020NovIns}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Banerjee, A. \emph{et al.} Novel Insights Into Immune
Systems of Bats. \emph{Frontiers in Immunology} \textbf{11}, 26 (2020).}

\leavevmode\hypertarget{ref-Gorbunova2020WorGoe}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Gorbunova, V., Seluanov, A. \& Kennedy, B. K. The World
Goes Bats: Living Longer and Tolerating Viruses. \emph{Cell Metabolism}
\textbf{32}, 31--43 (2020).}

\leavevmode\hypertarget{ref-Irving2021LesHos}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Irving, A. T., Ahn, M., Goh, G., Anderson, D. E. \&
Wang, L.-F. Lessons from the host defences of bats, a unique viral
reservoir. \emph{Nature} \textbf{589}, 363--370 (2021).}

\leavevmode\hypertarget{ref-Jebb2020SixRef}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Jebb, D. \emph{et al.} Six reference-quality genomes
reveal evolution of bat adaptations. \emph{Nature} \textbf{583},
578--584 (2020).}

\leavevmode\hypertarget{ref-MorenoSantillan2021LarGen}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Moreno Santillán, D. D. \emph{et al.} Large-scale genome
sampling reveals unique immunity and metabolic adaptations in bats.
\emph{Molecular Ecology} mec.16027 (2021)
doi:\href{https://doi.org/10.1111/mec.16027}{10.1111/mec.16027}.}

\leavevmode\hypertarget{ref-Muylaert2022PreFut}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Muylaert, R. L. \emph{et al.} Present and future
distribution of bat hosts of sarbecoviruses: Implications for
conservation and public health. \emph{Proceedings of the Royal Society
B: Biological Sciences} \textbf{289}, 20220397 (2022).}

\leavevmode\hypertarget{ref-Wang2018SerEvi}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Ramshaw2019DatGeo}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Ramshaw, R. E. \emph{et al.} A database of geopositioned
Middle East Respiratory Syndrome Coronavirus occurrences.
\emph{Scientific Data} \textbf{6}, 318 (2019).}

\leavevmode\hypertarget{ref-Lednicky2021IsoNov}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Lednicky, J. A. \emph{et al.} Isolation of a Novel
Recombinant Canine Coronavirus from a Visitor to Haiti: Further Evidence
of Transmission of Coronaviruses of Zoonotic Origin to Humans.
\emph{Clinical Infectious Diseases: An Official Publication of the
Infectious Diseases Society of America} ciab924 (2021)
doi:\href{https://doi.org/10.1093/cid/ciab924}{10.1093/cid/ciab924}.}

\leavevmode\hypertarget{ref-Vlasova2022AniAlp}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Vlasova, A. N. \emph{et al.} Animal alphacoronaviruses
found in human patients with acute respiratory illness in different
countries. \emph{Emerging Microbes \& Infections} \textbf{11}, 699--702
(2022).}

\leavevmode\hypertarget{ref-Shi2014DeeDiv}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022FulGen}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Hazarie2021IntPop}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Hazarie, S., Soriano-Paños, D., Arenas, A.,
Gómez-Gardeñes, J. \& Ghoshal, G. Interplay between population density
and mobility in determining the spread of epidemics in cities.
\emph{Communications Physics} \textbf{4}, 191 (2021).}

\leavevmode\hypertarget{ref-Xu2004EpiClu}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Peixoto2018SynEco}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Peixoto, F. P., Braga, P. H. P. \& Mendes, P. A
synthesis of ecological and evolutionary determinants of bat diversity
across spatial scales. \emph{BMC ecology} \textbf{18}, 18 (2018).}

\leavevmode\hypertarget{ref-Simmons2020BatSpe}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Simmons, N. B. \& Cirranello, A. L. Bat Species of the
World: A taxonomic and geographic database. \url{https://batnames.org/}
(2020).}

\leavevmode\hypertarget{ref-Kasso2013EcoEco}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Mello2011MisPar}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Voigt2016BatAnt}{}%
\CSLLeftMargin{38. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008BatLim}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013MosCon}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013MosInf}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Wu2021ComSur}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Carlson2022CliCha}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Alves2018GeoVar}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}

\leavevmode\hypertarget{ref-Treitler2016EffLoc}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Treitler, J. T., Heim, O., Tschapka, M. \& Jung, K. The
effect of local land use and loss of forests on bats and nocturnal
insects. \emph{Ecology and Evolution} \textbf{6}, 4289--4297 (2016).}

\leavevmode\hypertarget{ref-Johnson2020GloShi}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Johnson, C. K. \emph{et al.} Global shifts in mammalian
population trends reveal key predictors of virus spillover risk.
\emph{Proceedings of the Royal Society B: Biological Sciences}
\textbf{287}, 20192736 (2020).}

\leavevmode\hypertarget{ref-Gryseels2017WheVir}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Gryseels, S. \emph{et al.} When Viruses Don't Go Viral:
The Importance of Host Phylogeographic Structure in the Spatial Spread
of Arenaviruses. \emph{PLOS Pathogens} \textbf{13}, e1006073 (2017).}

\leavevmode\hypertarget{ref-Amman2011InvRol}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Amman, B. R. \emph{et al.} \emph{Investigating the role
of bats in emerging zoonoses: Balancing ecology, conservation and public
health interest}. (FAO, 2011).}

\leavevmode\hypertarget{ref-IUCN2021IucRed}{}%
\CSLLeftMargin{49. }
\CSLRightInline{IUCN. The IUCN Red List of Threatened Species.
\url{https://www.iucnredlist.org} (2021).}

\leavevmode\hypertarget{ref-RouaultEven2022GdaOgr}{}%
\CSLLeftMargin{50. }
\CSLRightInline{Rouault, E. \emph{et al.} \emph{GDAL/OGR Geospatial Data
Abstraction software Library}. (Zenodo, 2022).
doi:\href{https://doi.org/10.5281/ZENODO.5884351}{10.5281/ZENODO.5884351}.}

\leavevmode\hypertarget{ref-Faith1992ConEva}{}%
\CSLLeftMargin{51. }
\CSLRightInline{Faith, D. P. Conservation evaluation and phylogenetic
diversity. \emph{Biological Conservation} \textbf{61}, 1--10 (1992).}

\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
\CSLLeftMargin{52. }
\CSLRightInline{Upham, N. S., Esselstyn, J. A. \& Jetz, W. Inferring the
mammal tree: Species-level sets of phylogenies for questions in ecology,
evolution, and conservation. \emph{PLOS Biology} \textbf{17}, e3000494
(2019).}

\leavevmode\hypertarget{ref-Legendre2013BetDiv}{}%
\CSLLeftMargin{53. }
\CSLRightInline{Legendre, P. \& De Cáceres, M. Beta diversity as the
variance of community data: Dissimilarity coefficients and partitioning.
\emph{Ecology Letters} \textbf{16}, 951--963 (2013).}

\leavevmode\hypertarget{ref-Legendre2019SpaTem}{}%
\CSLLeftMargin{54. }
\CSLRightInline{Legendre, P. \& Condit, R. Spatial and temporal analysis
of beta diversity in the Barro Colorado Island forest dynamics plot,
Panama. \emph{Forest Ecosystems} \textbf{6}, 7 (2019).}

\leavevmode\hypertarget{ref-Dansereau2022EvaEco}{}%
\CSLLeftMargin{55. }
\CSLRightInline{Dansereau, G., Legendre, P. \& Poisot, T. Evaluating
ecological uniqueness over broad spatial extents using species
distribution modelling. \emph{Oikos} \textbf{n/a}, e09063 (2022).}

\leavevmode\hypertarget{ref-Albery2020PreGlo}{}%
\CSLLeftMargin{56. }
\CSLRightInline{Albery, G. F., Eskew, E. A., Ross, N. \& Olival, K. J.
Predicting the global mammalian viral sharing network using
phylogeography. \emph{Nature Communications} \textbf{11}, 2260 (2020).}

\leavevmode\hypertarget{ref-Seekell2018GeoLak}{}%
\CSLLeftMargin{57. }
\CSLRightInline{Seekell, D. A., Lapierre, J.-F. \& Cheruvelil, K. S. A
geography of lake carbon cycling. \emph{Limnology and Oceanography
Letters} \textbf{3}, 49--56 (2018).}

\leavevmode\hypertarget{ref-Gomulkiewicz2000HotSpo}{}%
\CSLLeftMargin{58. }
\CSLRightInline{Gomulkiewicz, R., Thompson, J. N., Holt, R. D., Nuismer,
S. L. \& Hochberg, M. E. Hot Spots, Cold Spots, and the Geographic
Mosaic Theory of Coevolution. \emph{The American Naturalist}
\textbf{156}, 156--174 (2000).}

\leavevmode\hypertarget{ref-Keke2010StuSki}{}%
\CSLLeftMargin{59. }
\CSLRightInline{Keke, S., Peng, Z. \& Guohui, L. Study on skin color
image segmentation used by Fuzzy-c-means arithmetic. in \emph{2010
Seventh International Conference on Fuzzy Systems and Knowledge
Discovery} vol. 2 612--615 (2010).}

\leavevmode\hypertarget{ref-Katoh2013MafMul}{}%
\CSLLeftMargin{60. }
\CSLRightInline{Katoh, K. \& Standley, D. M. MAFFT Multiple Sequence
Alignment Software Version 7: Improvements in Performance and Usability.
\emph{Molecular Biology and Evolution} \textbf{30}, 772--780 (2013).}

\leavevmode\hypertarget{ref-Nguyen2015IqtFas}{}%
\CSLLeftMargin{61. }
\CSLRightInline{Nguyen, L.-T., Schmidt, H. A., von Haeseler, A. \& Minh,
B. Q. IQ-TREE: A Fast and Effective Stochastic Algorithm for Estimating
Maximum-Likelihood Phylogenies. \emph{Molecular Biology and Evolution}
\textbf{32}, 268--274 (2015).}

\leavevmode\hypertarget{ref-Kalyaanamoorthy2017ModFas}{}%
\CSLLeftMargin{62. }
\CSLRightInline{Kalyaanamoorthy, S., Minh, B. Q., Wong, T. K. F., von
Haeseler, A. \& Jermiin, L. S. ModelFinder: Fast model selection for
accurate phylogenetic estimates. \emph{Nature Methods} \textbf{14},
587--589 (2017).}

\leavevmode\hypertarget{ref-Hoang2018UfbImp}{}%
\CSLLeftMargin{63. }
\CSLRightInline{Hoang, D. T., Chernomor, O., von Haeseler, A., Minh, B.
Q. \& Vinh, L. S. UFBoot2: Improving the Ultrafast Bootstrap
Approximation. \emph{Molecular Biology and Evolution} \textbf{35},
518--522 (2018).}

\leavevmode\hypertarget{ref-Isaac2007MamEdg}{}%
\CSLLeftMargin{64. }
\CSLRightInline{Isaac, N. J. B., Turvey, S. T., Collen, B., Waterman, C.
\& Baillie, J. E. M. Mammals on the EDGE: Conservation Priorities Based
on Threat and Phylogeny. \emph{PLOS ONE} \textbf{2}, e296 (2007).}

\leavevmode\hypertarget{ref-Kreft2007GloPat}{}%
\CSLLeftMargin{65. }
\CSLRightInline{Kreft, H. \& Jetz, W. Global patterns and determinants
of vascular plant diversity. \emph{Proceedings of the National Academy
of Sciences} \textbf{104}, 5925--5930 (2007).}

\leavevmode\hypertarget{ref-Kreft2010FraDel}{}%
\CSLLeftMargin{66. }
\CSLRightInline{Kreft, H. \& Jetz, W. A framework for delineating
biogeographical regions based on species distributions. \emph{Journal of
Biogeography} \textbf{37}, 2029--2053 (2010).}

\leavevmode\hypertarget{ref-Paradis2019ApeEnv}{}%
\CSLLeftMargin{67. }
\CSLRightInline{Paradis, E. \& Schliep, K. Ape 5.0: An environment for
modern phylogenetics and evolutionary analyses in R.
\emph{Bioinformatics} \textbf{35}, 526--528 (2019).}

>>>>

Subsequently, we tested the hypothesis that the biogeography of bat
betacoronaviruses should track the biogeography of their hosts. To test
this idea, we loosely adapted a method from,\textsuperscript{59,60} who
proposed a phylogenetic method for the delineation of animal
biogeographic regions. In their original method, a distance matrix -
where each row or column represents a geographic raster's grid cell, and
the dissimilarity values are the ``beta diversity similarity'' of their
community assemble - undergoes non-metric multidimensional scaling
(NMDS); the first two axes of the NMDS are projected geographically
using a four-color bivariate map. Here, we build on this idea with an
entirely novel methodology. First, we measure the phylogenetic distance
between the different viruses in the betacoronaviruses tree by using the
cophenetic function in \texttt{ape};\textsuperscript{61} subsequently,
we take a principal components analysis of that distance matrix (readily
interchangeable for NMDS in this case) to project the viral tree into an
n-dimensional space. We then take the first two principal components
and, as with the evolutionary distinctiveness analysis, aggregated these
to a mean host value and projected them using a four-color bivariate
map.

@@

\leavevmode\hypertarget{ref-Shi2014DeeDiv}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022FulGen}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Hazarie2021IntPop}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Hazarie, S., Soriano-Paños, D., Arenas, A.,
Gómez-Gardeñes, J. \& Ghoshal, G. Interplay between population density
and mobility in determining the spread of epidemics in cities.
\emph{Communications Physics} \textbf{4}, 191 (2021).}

\leavevmode\hypertarget{ref-Xu2004EpiClu}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Wang2018SerEvi}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Ramshaw2019DatGeo}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Ramshaw, R. E. \emph{et al.} A database of geopositioned
Middle East Respiratory Syndrome Coronavirus occurrences.
\emph{Scientific Data} \textbf{6}, 318 (2019).}

\leavevmode\hypertarget{ref-Lednicky2021IsoNov}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Lednicky, J. A. \emph{et al.} Isolation of a Novel
Recombinant Canine Coronavirus from a Visitor to Haiti: Further Evidence
of Transmission of Coronaviruses of Zoonotic Origin to Humans.
\emph{Clinical Infectious Diseases: An Official Publication of the
Infectious Diseases Society of America} ciab924 (2021)
doi:\href{https://doi.org/10.1093/cid/ciab924}{10.1093/cid/ciab924}.}

\leavevmode\hypertarget{ref-Vlasova2022AniAlp}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Vlasova, A. N. \emph{et al.} Animal alphacoronaviruses
found in human patients with acute respiratory illness in different
countries. \emph{Emerging Microbes \& Infections} \textbf{11}, 699--702
(2022).}

\leavevmode\hypertarget{ref-Letko2020BatVir}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Letko, M., Seifert, S. N., Olival, K. J., Plowright, R.
K. \& Munster, V. J. Bat-borne virus diversity, spillover and emergence.
\emph{Nature Reviews Microbiology} \textbf{18}, 461--471 (2020).}

\leavevmode\hypertarget{ref-VanBrussel2022ZooDis}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Van Brussel, K. \& Holmes, E. C. Zoonotic disease and
virome diversity in bats. \emph{Current Opinion in Virology}
\textbf{52}, 192--202 (2022).}

\leavevmode\hypertarget{ref-Peixoto2018SynEco}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Peixoto, F. P., Braga, P. H. P. \& Mendes, P. A
synthesis of ecological and evolutionary determinants of bat diversity
across spatial scales. \emph{BMC ecology} \textbf{18}, 18 (2018).}

\leavevmode\hypertarget{ref-Simmons2020BatSpe}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Simmons, N. B. \& Cirranello, A. L. Bat Species of the
World: A taxonomic and geographic database. \url{https://batnames.org/}
(2020).}

\leavevmode\hypertarget{ref-Kasso2013EcoEco}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Mello2011MisPar}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Voigt2016BatAnt}{}%
\CSLLeftMargin{32. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008BatLim}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013MosCon}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013MosInf}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Wu2021ComSur}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Carlson2022CliCha}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Alves2018GeoVar}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}

\leavevmode\hypertarget{ref-Treitler2016EffLoc}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Treitler, J. T., Heim, O., Tschapka, M. \& Jung, K. The
effect of local land use and loss of forests on bats and nocturnal
insects. \emph{Ecology and Evolution} \textbf{6}, 4289--4297 (2016).}

\leavevmode\hypertarget{ref-Johnson2020GloShi}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Johnson, C. K. \emph{et al.} Global shifts in mammalian
population trends reveal key predictors of virus spillover risk.
\emph{Proceedings of the Royal Society B: Biological Sciences}
\textbf{287}, 20192736 (2020).}

\leavevmode\hypertarget{ref-Gryseels2017WheVir}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Gryseels, S. \emph{et al.} When Viruses Don't Go Viral:
The Importance of Host Phylogeographic Structure in the Spatial Spread
of Arenaviruses. \emph{PLOS Pathogens} \textbf{13}, e1006073 (2017).}

\leavevmode\hypertarget{ref-Amman2011InvRol}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Amman, B. R. \emph{et al.} \emph{Investigating the role
of bats in emerging zoonoses: Balancing ecology, conservation and public
health interest}. (FAO, 2011).}

\leavevmode\hypertarget{ref-IUCN2021IucRed}{}%
\CSLLeftMargin{43. }
\CSLRightInline{IUCN. The IUCN Red List of Threatened Species.
\url{https://www.iucnredlist.org} (2021).}

\leavevmode\hypertarget{ref-RouaultEven2022GdaOgr}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Rouault, E. \emph{et al.} \emph{GDAL/OGR Geospatial Data
Abstraction software Library}. (Zenodo, 2022).
doi:\href{https://doi.org/10.5281/ZENODO.5884351}{10.5281/ZENODO.5884351}.}

\leavevmode\hypertarget{ref-Faith1992ConEva}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Faith, D. P. Conservation evaluation and phylogenetic
diversity. \emph{Biological Conservation} \textbf{61}, 1--10 (1992).}

\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Upham, N. S., Esselstyn, J. A. \& Jetz, W. Inferring the
mammal tree: Species-level sets of phylogenies for questions in ecology,
evolution, and conservation. \emph{PLOS Biology} \textbf{17}, e3000494
(2019).}

\leavevmode\hypertarget{ref-Legendre2013BetDiv}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Legendre, P. \& De Cáceres, M. Beta diversity as the
variance of community data: Dissimilarity coefficients and partitioning.
\emph{Ecology Letters} \textbf{16}, 951--963 (2013).}

\leavevmode\hypertarget{ref-Legendre2019SpaTem}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Legendre, P. \& Condit, R. Spatial and temporal analysis
of beta diversity in the Barro Colorado Island forest dynamics plot,
Panama. \emph{Forest Ecosystems} \textbf{6}, 7 (2019).}

\leavevmode\hypertarget{ref-Dansereau2022EvaEco}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Dansereau, G., Legendre, P. \& Poisot, T. Evaluating
ecological uniqueness over broad spatial extents using species
distribution modelling. \emph{Oikos} \textbf{n/a}, e09063 (2022).}

\leavevmode\hypertarget{ref-Albery2020PreGlo}{}%
\CSLLeftMargin{50. }
\CSLRightInline{Albery, G. F., Eskew, E. A., Ross, N. \& Olival, K. J.
Predicting the global mammalian viral sharing network using
phylogeography. \emph{Nature Communications} \textbf{11}, 2260 (2020).}

\leavevmode\hypertarget{ref-Seekell2018GeoLak}{}%
\CSLLeftMargin{51. }
\CSLRightInline{Seekell, D. A., Lapierre, J.-F. \& Cheruvelil, K. S. A
geography of lake carbon cycling. \emph{Limnology and Oceanography
Letters} \textbf{3}, 49--56 (2018).}

\leavevmode\hypertarget{ref-Gomulkiewicz2000HotSpo}{}%
\CSLLeftMargin{52. }
\CSLRightInline{Gomulkiewicz, R., Thompson, J. N., Holt, R. D., Nuismer,
S. L. \& Hochberg, M. E. Hot Spots, Cold Spots, and the Geographic
Mosaic Theory of Coevolution. \emph{The American Naturalist}
\textbf{156}, 156--174 (2000).}

\leavevmode\hypertarget{ref-Keke2010StuSki}{}%
\CSLLeftMargin{53. }
\CSLRightInline{Keke, S., Peng, Z. \& Guohui, L. Study on skin color
image segmentation used by Fuzzy-c-means arithmetic. in \emph{2010
Seventh International Conference on Fuzzy Systems and Knowledge
Discovery} vol. 2 612--615 (2010).}

\leavevmode\hypertarget{ref-Katoh2013MafMul}{}%
\CSLLeftMargin{54. }
\CSLRightInline{Katoh, K. \& Standley, D. M. MAFFT Multiple Sequence
Alignment Software Version 7: Improvements in Performance and Usability.
\emph{Molecular Biology and Evolution} \textbf{30}, 772--780 (2013).}

\leavevmode\hypertarget{ref-Nguyen2015IqtFas}{}%
\CSLLeftMargin{55. }
\CSLRightInline{Nguyen, L.-T., Schmidt, H. A., von Haeseler, A. \& Minh,
B. Q. IQ-TREE: A Fast and Effective Stochastic Algorithm for Estimating
Maximum-Likelihood Phylogenies. \emph{Molecular Biology and Evolution}
\textbf{32}, 268--274 (2015).}

\leavevmode\hypertarget{ref-Kalyaanamoorthy2017ModFas}{}%
\CSLLeftMargin{56. }
\CSLRightInline{Kalyaanamoorthy, S., Minh, B. Q., Wong, T. K. F., von
Haeseler, A. \& Jermiin, L. S. ModelFinder: Fast model selection for
accurate phylogenetic estimates. \emph{Nature Methods} \textbf{14},
587--589 (2017).}

\leavevmode\hypertarget{ref-Hoang2018UfbImp}{}%
\CSLLeftMargin{57. }
\CSLRightInline{Hoang, D. T., Chernomor, O., von Haeseler, A., Minh, B.
Q. \& Vinh, L. S. UFBoot2: Improving the Ultrafast Bootstrap
Approximation. \emph{Molecular Biology and Evolution} \textbf{35},
518--522 (2018).}

\leavevmode\hypertarget{ref-Isaac2007MamEdg}{}%
\CSLLeftMargin{58. }
\CSLRightInline{Isaac, N. J. B., Turvey, S. T., Collen, B., Waterman, C.
\& Baillie, J. E. M. Mammals on the EDGE: Conservation Priorities Based
on Threat and Phylogeny. \emph{PLOS ONE} \textbf{2}, e296 (2007).}

\leavevmode\hypertarget{ref-Kreft2007GloPat}{}%
\CSLLeftMargin{59. }
\CSLRightInline{Kreft, H. \& Jetz, W. Global patterns and determinants
of vascular plant diversity. \emph{Proceedings of the National Academy
of Sciences} \textbf{104}, 5925--5930 (2007).}

\leavevmode\hypertarget{ref-Kreft2010FraDel}{}%
\CSLLeftMargin{60. }
\CSLRightInline{Kreft, H. \& Jetz, W. A framework for delineating
biogeographical regions based on species distributions. \emph{Journal of
Biogeography} \textbf{37}, 2029--2053 (2010).}

\leavevmode\hypertarget{ref-Paradis2019ApeEnv}{}%
\CSLLeftMargin{61. }
\CSLRightInline{Paradis, E. \& Schliep, K. Ape 5.0: An environment for
modern phylogenetics and evolutionary analyses in R.
\emph{Bioinformatics} \textbf{35}, 526--528 (2019).}
